High-Dim Project

### 2014-12-18 highdim-paper/paper.tex
intro
added intro and names

\author{name1 \\
  Columbia University\\
  {\small \tt uni1@columbia.edu} \\\And
  name2 \\
  Columbia University\\
  {\small \tt uni2@columbia.edu} \\\And
  name3\\
  Columbia University\\
  {\small \tt uni3@columbia.edu} \\}
\date{}

@@

\section{Introduction}

>>>>

\author{Chris Kedzie \\
  Columbia University\\
  {\small \tt kedzie@cs.columbia.edu} \\\And
  Dahong Liu \\
  Columbia University\\
  {\small \tt dl2868@columbia.edu} \\\And
  Xiao Zhu\\
  Columbia University\\
  {\small \tt xz2362@columbia.edu} \\\And
  Yichi Zhang\\
  Columbia University\\
  {\small \tt yz2657@columbia.edu} \\}
\date{}

@@

\section{Introduction}
We motivate our project by considering the text classification problem: 
can we accurately classify text documents by topic. With the rapid growth 
of online information, text categorization has become one of the key techniques 
for handling and organizing text data. Text categorization techniques are used 
not only to filter spam emails, as we are mostly familiar, but also to classify 
news stories, to find interesting information on the WWW, and to guide a 
user's search through hypertext. Since building text classifiers by hand is 
difficult and time-consuming, it is advantageous to learn classifiers from examples. \\

In this project we will use the ''20 Newsgroups'' dataset, popular in machine 
learning literature, to explore some variants of latent group lasso for text classification. 
This dataset contains about 20,000 documents split roughly evenly amongst the 20 
predefined topics. Every training example comes in the form of a document-term 
matrix $\mathbf{M}$ that is $D\times V$ where $D=11307$. The vocabulary 
size $V= 61188$ words. \\

In section 2, we will provide some background on latent group lasso and 
multiclass classification. Latent group Lasso is based on applying the usual 
group Lasso penalty on a set of latent variables when groups are overlapping.
In section 3, we will present our model, which uses hinge loss for training classifiers. 
The following sections will include detailed explanations of our datasets and the 
results we gathered.
